Type-Safe Modular Parsing

### 2016-12-22 paper/sections/OpenRecursion.tex
Update the tex template. Minor comments on Overview.
Fix

Open recursion is known as a useful feature that one method body can
``invoke another method of the same object via a special variable
called \lstinline{self} or, in some languages,
\lstinline[keywords={}]{this}'' (by Ralf Hinze)\bruno{this is not how we cite references!}. The interesting thing
is that such a variable \lstinline{self} is late-bound, or open to the
recursion, which means it can integrate some additional features
defined later, while existing methods that take \lstinline{self} as a
parameter can simply delegate their known cases to it.

@@

\lstinputlisting[linerange=34-40]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB

@@

\lstinputlisting[linerange=44-51]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB2
\bruno{Fix should be replaces by Open. Please coordinate with Huang to
ensure that your code and his code are coherent (i.e you use same
names and same conventions),}
\noindent This alternative implementation has an extra argument
\lstinline{self}, which serves as an explicit self-reference. In the 
definition of the function, direct recursive calls are replaced by 
calls to the self reference.

\paragraph{Closing the Open Recursion} An implementation of
 standard the standard Fibonacci function is recovered by closing 
the open recursion using a \emph{lazy fixpoint combinator}:
\bruno{definition of fib with fix here.}

@@

\lstinputlisting[linerange=27-30]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIX
\bruno{can be defined in a single line.}
\noindent Note that the function \lstinline{f} has a by-name parameter 
of type \lstinline{"=>} \lstinline{A"}. This is necessary to ensure
termination of well-founded recursive calls. In such cases, 
there are some base cases (like the first two in
\lstinline{fib2}) which stop the recursion in their branches, and the 
evaluation is finally reduced to those cases.

@@

Next we define a more general combinator \lstinline{merge} for open recursion. It is similar to the \lstinline{*} above, but instead of putting two values in a pair by default, \lstinline{merge} takes a parameter called \lstinline{op}, which tells the associative operation of two results. The definition is straightforward:
\lstinputlisting[linerange=66-66]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_MERGE

>>>>

Open recursion is known as a useful feature that one method body can
``invoke another method of the same object via a special variable
called \lstinline{self} or, in some languages,
\lstinline[keywords={}]{this}'' (by Ralf Hinze)\bruno{this is not how we cite references!}
\haoyuan{It's a talk by him, I'm not sure how to cite it, see URL: http://www.cs.ox.ac.uk/ralf.hinze/talks/}. The interesting thing
is that such a variable \lstinline{self} is late-bound, or open to the
recursion, which means it can integrate some additional features
defined later, while existing methods that take \lstinline{self} as a
parameter can simply delegate their known cases to it.

@@

\lstinputlisting[linerange=31-37]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB

@@

\lstinputlisting[linerange=41-47]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB2
\bruno{Fix should be replaces by Open. Please coordinate with Huang to
ensure that your code and his code are coherent (i.e you use same
names and same conventions),}
\noindent This alternative implementation has an extra argument
\lstinline{self}, which serves as an explicit self-reference. In the
definition of the function, direct recursive calls are replaced by
calls to the self reference.

\paragraph{Closing the Open Recursion} An implementation of
 the standard Fibonacci function is recovered by closing
the open recursion using a \emph{lazy fixpoint combinator}:
\bruno{definition of fib with fix here.}

\lstinputlisting[linerange=51-51]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB_FIX

@@

\lstinputlisting[linerange=27-27]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIX
\bruno{can be defined in a single line.}
\noindent Note that the function \lstinline{f} has a by-name parameter
of type \lstinline{"=>} \lstinline{T"}. This is necessary to ensure
termination of well-founded recursive calls. In such cases,
there are some base cases (like the first two in
\lstinline{fib2}) which stop the recursion in their branches, and the
evaluation is finally reduced to those cases.

@@

Next we define a more general combinator \lstinline{merge} for open recursion. It is similar to the \lstinline{*} above, but instead of putting two values in a pair by default, \lstinline{merge} takes a parameter called \lstinline{op}, which tells the associative operation of two results. The definition is straightforward:
\lstinputlisting[linerange=66-67]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_MERGE

### 2016-12-22 paper/sections/PackratParsers.tex
Fix

Note that the code should be defined in an enclosing type that extends
\lstinline{scala.util.parsing.combinator.syntactical.StandardTokenParsers}
for lexing and
\lstinline{scala.util.parsing.combinator.PackratParsers} for Packrat
parsers.
The first two lines are used for lexing. The third line defines a
parser which can, for instance, parse \lstinline{"str(5)"} and produce
the string \lstinline{"5"}. In \lstinline{StandardTokenParsers} there
are a number of basic parsers, such as \lstinline{numericLit} that
parses integers, and \lstinline{stringLit} that parsers string
literals. Moreover, in Scala the syntax for parsing
is quite concise and clear, as shown above, with the help of
parser combinators. The combinators \lstinline{~>} and \lstinline{<~} only collect
results from the parts that arrows point to, and the combinator \lstinline{^^} is
followed by a function which is applied to a parser to return new
values. Finally, a generic \lstinline{runParser}
function is used for testing:

\lstinputlisting[linerange=16-19]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=PACKRAT_RUNPARSER
Now \lstinline{runParser(p)("str(5)")} prints out \lstinline{"5"} as expected.

>>>>

Note that the code should be defined in an enclosing type that extends
\lstinline{scala.util.parsing.combinator.syntactical.StandardTokenParsers}
for lexing and
\lstinline{scala.util.parsing.combinator.PackratParsers} for Packrat
parsers.
The first two lines are used for lexing. The third line defines a
parser which can, for instance, parse \lstinline{"str(5)"} and produce
the string \lstinline{"5"}. In \lstinline{StandardTokenParsers} there
are a number of basic parsers, such as \lstinline{numericLit} that
parses integers, and \lstinline{stringLit} that parsers string
literals. Moreover, in Scala the syntax for parsing
is quite concise and clear, as shown above, with the help of
parser combinators. The combinators \lstinline{~>} and \lstinline{<~} only collect
results from the parts that arrows point to, and the combinator \lstinline{^^} is
followed by a function which is applied to a parser to return new
values. Finally, a generic \inlinecode{parse}
function is used for testing:

\lstinputlisting[linerange=16-19]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=PACKRAT_RUNPARSER
Now \lstinline{parse(p)("str(5)")} produces \lstinline{"5"} as expected.
